Project-I by Group MexicoCity

### 2014-11-20 Project 1/report/paper.tex
PROJECT II STARTING

We then found that, since Pearson correlation predicted better correlation of square roots than squares but squares were actually better able to decrease test error, it might be a good idea to include 3rd degree transforms of the 11th and 24th variables for logistic regression. After having added them, the test error increased to 0.26656. Thus taking higher orders doesn’t seem to help. We then tried to include a dummy variable transform, but that increased the test error significantly to 0.32625, therefore we’re not going to use them.
\subsection{Penalized logistic regression}
We could improve the test error by cross-validation. The Figure \ref{fig:crossval} shows the three different tests error RMSE, 0-1 loss and log loss. We used different numbers of seeds to have a better prediction for our test error. For RMSE and 0-1 loss, we tried to change the range of the $\lambda$ parameter but we got the same curve.
\begin{figure}
\centering
\subfigure[0-1 loss]{\includegraphics[width=0.6\textwidth]{images/penLogRegCrossVall01Loss.jpg}}
\subfigure[rmse]{\includegraphics[width=0.6\textwidth]{images/penLogRegrmse.jpg}}
\subfigure[log loss]{\includegraphics[width=0.6\textwidth]{images/penLogRegLogloss.jpg}}
\caption{Cross-validation : penalized logistic regression with different lambda values}
\label{fig:crossval}
\end{figure} 
\section{Summary}
As we have seen, the cross validation helps to have a better test error.\\
We obtained these RMSE for regression.
\begin{description}
\item[leastSquaresGD] We achieved a RMSE of 0.6852
\item[leastSquares] We achieved a RMSE of 0.3317
\item[RidgeRegression] We achieved a RMSE of 0.3073
\end{description}
For the regression, we saw that the best method was Ridge Regression. The best parameter was $\lambda =  39.0694$ and we achieved a test error of 0.3073. This is obtained by removing the categorical, removing the un-correlated variables and using the cube of the 18th and the degree 6 with the 34th variable.

>>>>

We then found that, since Pearson correlation predicted better correlation of square roots than squares but squares were actually better able to decrease test error, it might be a good idea to include 3rd degree transforms of the 11th and 24th variables for logistic regression. After having added them, the test error increased to 0.26656. Thus taking higher orders doesn’t seem to help. We then tried to include a dummy variable transform, but that increased the test error significantly to 0.32625, therefore we’re not going to use them.
\subsection{Penalized logistic regression}
We could improve the test error by cross-validation. The Figure \ref{fig:crossval} shows the three different tests error RMSE, 0-1 loss and log loss. We used different numbers of seeds to have a better prediction for our test error. For RMSE and 0-1 loss, we tried to change the range of the $\lambda$ parameter but we got the same curve.
\begin{figure}
\centering
\subfigure[0-1 loss]{\includegraphics[width=0.6\textwidth]{images/penLogRegCrossVall01Loss.jpg}}
\subfigure[rmse]{\includegraphics[width=0.6\textwidth]{images/penLogRegrmse.jpg}}
\subfigure[log loss]{\includegraphics[width=0.6\textwidth]{images/penLogRegLogloss.jpg}}
\caption{Cross-validation : penalized logistic regression with different lambda values}
\label{fig:crossval}
\end{figure} 
\section{Summary}
As we have seen, the cross validation helps to have a better test error.\\
We obtained these RMSE for regression.
\begin{description}
\item[leastSquaresGD] We achieved a RMSE of 0.6852
\item[leastSquares] We achieved a RMSE of 0.3317
\item[RidgeRegression] We achieved a RMSE of 0.3073
\end{description}
For the regression, we saw that the best method was Ridge Regression. The best parameter was $\lambda =  39.0694$ and we achieved a test error of 0.3073. This is obtained by removing the categorical, removing the un-correlated variables and using the cube of the 18th and up to the degree 6 with the 34th variables.
